---
title: "paper"
format: html
editor: visual
---

### Background

This project recreates a graph that shows chemical concentrations before and after Hurricane Hugo in 4 streams in Bisley, Puerto Rico.
More specifically, it recreates Figure 3. from "Effects of Hurricane Disturbance on Stream Water Concentrations and Fluxes in Eight Tropical Forest Watersheds of the Luquillo Experimental Forest, Puerto Rico" by Douglas A. Schaefer, William H. McDowell, Fredrick N. Scatena and Clyde E. Asbury (2000) [https://doi.org/10.1017/s0266467400001358]

### Data

Data is taken from the Environmental Data Initiative [https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-luq.20.4923064]

### Methods
This creates the function moving-average.R, which takes the 9 week moving averages of the ion concentrations from the stream data. 
This is placed inside the "R" folder that defines functions.


This loads tidyverse functions, moving-average function, stores all 4 stream data into variables, and then turns the data all into moving averages.
```{r}
library(tidyverse)
print("start")
source("../R/moving-average.R")
source("../1_clean_data.R")

print("step 2")
BQ1 <- read_csv(
  "../data/QuebradaCuenca1-Bisley.csv",
  na = c("", "NA", "ND"))
BQ2 <- read_csv(
  "../data/QuebradaCuenca2-Bisley.csv",
  na = c("", "NA", "ND"))
BQ3 <- read_csv(
  "../data/QuebradaCuenca3-Bisley.csv",
  na = c("", "NA", "ND"))
PRM <- read_csv(
  "../data/RioMameyesPuenteRoto.csv",
  na = c("", "NA", "ND"))
print("end")

BQ1_Avg <- moving_average(BQ1)
BQ2_Avg <- moving_average(BQ2)
BQ3_Avg <- moving_average(BQ3)
PRM_Avg <- moving_average(PRM)
```

### Results
#### ggplot creation

```{r}
ggplot(
  data = Final_Data,
  mapping = aes(
    x = window_start,
    y = Concentration,
    linetype = Sample_ID,
    color = Sample_ID
  )
) + 
  geom_line() +
  facet_wrap("Ion", scales = "free", ncol = 1, strip.position = "left")
```


