---
title: "Recreating Figure 3 from Schaefer et al. (2000)"
author: Liam Sarmiento
format: html
editor: visual
---
### Background

This project recreates a graph that shows chemical concentrations before and after Hurricane Hugo in 4 streams in Bisley, Puerto Rico.
More specifically, it recreates Figure 3. from "Effects of Hurricane Disturbance on Stream Water Concentrations and Fluxes in Eight Tropical Forest Watersheds of the Luquillo Experimental Forest, Puerto Rico" by Douglas A. Schaefer, William H. McDowell, Fredrick N. Scatena and Clyde E. Asbury (2000) [https://doi.org/10.1017/s0266467400001358]

### Data

Data is taken from the Environmental Data Initiative [https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-luq.20.4923064]
The four stream data are taken from the folder "data/knb-lter-luq.20.4923064" and are as follows:
-QuebradaCuenca1-Bisley.csv
-QuebradaCuenca2-Bisley.csv
-QuebradaCuenca3-Bisley.csv
-RioMameyesPuenteRoto.csv


### Methods
The data is sorted into four csv's for each of the streams within R. The moving-average.R function takes a 9 week moving average of each ion concentration. Data has also been cut to include only dates from 1988 to mid 1994. ggplot2 was used to render the graph.

This loads tidyverse functions and pulls the already cleaned data.
```{r}
#| output: false
library(tidyverse)
Final_Data <- read_csv("../output/clean_data.csv")
```

### Results
#### ggplot creation
```{r}
#| echo: false
#| warning: false
ggplot(
  data = Final_Data,
  mapping = aes(
    x = window_start,
    y = Concentration,
    linetype = Sample_ID,
    color = Sample_ID
  )
) + 
  geom_line() +
  facet_wrap("Ion", scales = "free", ncol = 1, strip.position = "left") +
  labs(title = "Hurricane effects on stream chemistry", x = "Years") +
  geom_vline(xintercept = 7201, linetype = "longdash")
```

## References

https://doi.org/10.1017/s0266467400001358

https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-luq.20.4923064